Estimating Predictive Rate-Distortion Curves via Neural Variational Inference

### 2019-06-17 paper.tex
Updates from Overleaf

Training used Early Stopping using the development set, as described in Section~\ref{sec:parameter-estimation}.
Models were trained on a TITAN Xp graphics card.
\mhahn{TODO number of epochs, training time comparable to OCF}

On English word-level modeling, training took a median number of 9 epochs (max 467 epochs) and 5 minutes (max 126 minutes).

@@

\begin{figure*}
\centering
\begin{tabular}{cc}
&\textbf{Past:} within minutes after the stock market closed friday , i called sen. bill bradley of new \\
&\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_0.png}\\
&\textbf{Past:} asset you own would be worth more if the government suddenly announced that if you sold \\
&\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_20.png}\\
&\textbf{Past:} he thinks , when the white house is forced to ask for higher taxes to meet \\
&\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_31.png} \\
&\textbf{Past:} to be dealt with by the oct. 15 deadline , and these senate democrats refused to \\
&\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_6.png}
\end{tabular}

	\caption{Four example outputs from English word-level modeling, with low rate ($\log \frac{1}{\lambda} = 1$; red, dotted), medium rate ($\log \frac{1}{\lambda} = 3$; green, dashed), high rate ($\log \frac{1}{\lambda} = 5$; blue, solid). For each sample, we provide the prior context $\finitepast$ (top), and the per-word cross-entropies (in nats) on the future words $\finitefuture$ (bottom). \rljf{Figure needs y axis label and a legend to explain the meanings of the different colors}
	}\label{fig:samples-ptb}
\end{figure*}

>>>>

Training used Early Stopping using the development set, as described in Section~\ref{sec:parameter-estimation}.
Models were trained on a TITAN Xp graphics card.

\mhahn{TODO number of epochs, training time comparable to OCF}
On Even Process and Random Insertion Process, OCF takes at most a few seconds at $M \leq 5$.
On English word-level modeling, training took a median number of 9 epochs (max 467 epochs) and 5 minutes (max 126 minutes).

@@

\begin{figure*}
\centering
\begin{tabular}{c}
\textbf{Past:} within minutes after the stock market closed friday , i called sen. bill bradley of new \\
\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_0.png}\\
\textbf{Past:} asset you own would be worth more if the government suddenly announced that if you sold \\
\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_20.png}\\
\textbf{Past:} he thinks , when the white house is forced to ask for higher taxes to meet \\
\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_31.png} \\
\textbf{Past:} to be dealt with by the oct. 15 deadline , and these senate democrats refused to \\
\includegraphics[width=0.9\textwidth]{code/nprd/figures/sample_6.png} \\
\textbf{\textcolor{red}{- - - -}}\ \ Low rate ($\log \frac{1}{\lambda}=1.0$)\ \ \ \ \ \ 
\textbf{\textcolor{olive}{-- - --}}\ \ Median rate ($\log \frac{1}{\lambda}=3.0$)\ \ \ \ \ \ 
\textbf{\textcolor{blue}{------}}\ \ High rate ($\log \frac{1}{\lambda}=5.0$)
\end{tabular}

	\caption{Four example outputs from English word-level modeling, with low rate ($\log \frac{1}{\lambda} = 1$; red, dotted), medium rate ($\log \frac{1}{\lambda} = 3$; green, dashed), high rate ($\log \frac{1}{\lambda} = 5$; blue, solid). For each sample, we provide the prior context $\finitepast$ (top), and the per-word cross-entropies (in nats) on the future words $\finitefuture$ (bottom). %\rljf{Figure needs y axis label and a legend to explain the meanings of the different colors}
	}\label{fig:samples-ptb}
\end{figure*}
